Models of gravitational lens candidates from Space Warps CFHTLS

### 2017-08-27 parts/summary.tex
discussion about criteria

To assists volunteer modellers assessing their models, we introduce a
set of diagnostics allowing the qualification of the lenses and the
generated models and present them alongside the generated models. At a
later stage, we encourage modellers to apply those diagnostics
themselves to get a preliminary feedback on the plausibility of their
models.

>>>>

To assists volunteer modellers assessing their models, we introduce a
set of diagnostics allowing the qualification of the lenses and the
generated models and present them alongside the generated models. At a
later stage, we encourage modellers to apply those diagnostics
themselves to get a preliminary feedback on the plausibility of their
models and possibly suggest additional diagnostics.

The diagnostics (i) -- (iv) turned out to be useful for evaluating how difficult a system is to model, but they weren't necessary conditions for a promising model.
They can help select systems to present to novice volunteers to introduce them to the modelling process.
Diagnostics (v) and (vi) on the other hand can be considered as necessary criteria for a good model.
Volunteers employed those to evaluate their models and they turned out to be easy enough to grasp for new volunteers.
The halo-matching index $\haloindex$, diagnostic (vii), is an interesting criterion that might be useful for volunteers, but needs further investigation to be established.
